Refugees in Toronto's Shelters: Investigating Refugee Access and

### 2024-01-23 outputs/paper/paper.qmd
Added Title

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Krishiv Jain
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Refugees in Toronto's Shelters: Investigating Refugee Access and 
Discrimination, and Unraveling Media Narratives"
author: 
  - Krishiv Jain
thanks: "Code and data are available at: 
https://github.com/Krishiv-J/Toronto-Refugee-Shelter.git"
date: 23/01/24
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
